Transcriptional dynamics of influenza virus infection in single cells

### 2017-09-01 paper/paper.tex
a few minor citation additions, only had time to look at very beginning so far

\subsection{Strategy to measure mRNA in single virus-infected cells.}
We performed single-cell mRNA sequencing using a droplet-based system that physically isolates individual cells prior to reverse transcription~\citep{Macosko:2015ht,Klein:2015ki}.
Each droplet is associated with a unique \emph{cell barcode} that tags all mRNAs from that cell during reverse-transcription.
A random \emph{unique molecular identifier (UMI)} is additionally appended to each mRNA molecule during reverse transcription.
The 3' ends of the mRNAs are sequenced and mapped to the human and influenza virus transcriptomes to determine transcript identities.
This information is combined with that provided by the UMIs and cell barcodes to quantify the number of molecules of each mRNA species that have been captured for each cell.

@@

We took care to generate stocks of virus that were relatively ``pure'' of defective particles.
Stocks of viruses typically contain an array of biologically active viral particles, some of which are defective for replication owing to mutations or deletions in essential viral genes ~\citep{Brooke:2014ch,Fonville:2015cg,Lauring:2010if,Dimmock:2014dk}.
These defective particles become prevalent when a virus is grown at high multiplicity of infection (MOI), where complementation permits the growth of otherwise deleterious genotypes ~\citep{Lopez:2014en}.
To minimize the levels of defective particles, we propagated our viral stocks at low MOI for a relatively brief period of time~\citep{Xue:2016bw}.
We then validated that our stocks exhibited greater purity of infectious particles than a stock propagated at high MOI by verifying that they had a higher ratio of infectious particles to both virion RNA (Figure~\ref{fig:viruspopulations}A) and particles capable of inducing expression of a single viral protein (Figure~\ref{fig:viruspopulations}B).
In addition, viral stocks with many defective particles are more immunostimulatory~\citep{Tapia:2013kf}.
We confirmed that our viral stocks induced much less interferon than a stock propagated at higher MOI (Figure~\ref{fig:viruspopulations}C).

>>>>

\subsection{Strategy to measure mRNA in single virus-infected cells.}
We performed single-cell mRNA sequencing using a droplet-based system that physically isolates individual cells prior to reverse transcription~\citep{zheng2017massively,Macosko:2015ht,Klein:2015ki}.
Each droplet is associated with a unique \emph{cell barcode} that tags all mRNAs from that cell during reverse-transcription.
A random \emph{unique molecular identifier (UMI)} is additionally appended to each mRNA molecule during reverse transcription.
The 3' ends of the mRNAs are sequenced and mapped to the human and influenza virus transcriptomes to determine transcript identities.
This information is combined with that provided by the UMIs and cell barcodes to quantify the number of molecules of each mRNA species that have been captured for each cell.

@@

We took care to generate stocks of virus that were relatively ``pure'' of defective particles.
Stocks of viruses typically contain an array of biologically active viral particles, some of which are defective for replication owing to mutations or deletions in essential viral genes ~\citep{von1954incomplete,huang1970defective,Brooke:2014ch,Fonville:2015cg,Lauring:2010if,Dimmock:2014dk}.
These defective particles become prevalent when a virus is grown at high multiplicity of infection (MOI), where complementation permits the growth of otherwise deleterious genotypes ~\citep{Lopez:2014en}.
To minimize the levels of defective particles, we propagated our viral stocks at low MOI for a relatively brief period of time~\citep{Xue:2016bw}.
We then validated that our stocks exhibited greater purity of infectious particles than a stock propagated at high MOI by verifying that they had a higher ratio of infectious particles to both virion RNA (Figure~\ref{fig:viruspopulations}A) and particles capable of inducing expression of a single viral protein (Figure~\ref{fig:viruspopulations}B).
In addition, viral stocks with many defective particles are more immunostimulatory~\citep{Tapia:2013kf}.
We confirmed that our viral stocks induced much less interferon than a stock propagated at higher MOI (Figure~\ref{fig:viruspopulations}C).
